External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-13 CVPR2017_Review_Unified.tex
add

Most of the denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN). Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise. As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}. One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.

There have been a few methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite,neatimage} developed for real noisy image denoising. Almost all of these methods follow a two-stage framework: first estimate the parameters of the assumed noise model (usually Gaussian  or mixture of Gaussians (MoG)), and then perform denoising with the estimated noise model. Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoised results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}.\ One can see that these two methods do not perform well on this noisy image either.

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3.5mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NC \cite{noiseclinic,ncwebsite}: 35.33dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of a cropped part from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

This work aims to develop a robust solution for real noisy image denoising without explicitly assuming certain noise models.\ To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.\ The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}.\ We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior.\ The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then a hybrid orthogonal dictionary (HOD) is learned as the internal prior for image denoising. Our proposed denoising method is simple and efficient, yet our extensive experiments on real noisy images clearly demonstrate its better denoising performance than the current state-of-the-arts.

>>>>

Most of the denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN). Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise. As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf} and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}. One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.

There have been a few methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite,neatimage} developed for real noisy image denoising. Almost all of these methods follow a two-stage framework: first estimate the parameters of the assumed noise model (usually Gaussian  or mixture of Gaussians (MoG)), and then perform denoising with the estimated noise model. Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoising results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}.\ One can see that these two methods do not perform well on this noisy image either.

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3.5mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NC \cite{noiseclinic,ncwebsite}: 35.33dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

This work aims to develop a robust denoiser for real noisy image denoising without explicitly assuming certain noise models.\ To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal priors from the given noisy image.\ The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}.\ We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior.\ The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then an external-internal hybrid orthogonal dictionary is learned as the final prior for image denoising. Our proposed denoising method is simple and efficient, yet our extensive experiments on real noisy images clearly demonstrate its better denoising performance than the current state-of-the-arts.
